Chord: A Static and Dynamic Program Analysis Framework for Java

### 2010-04-02 main/doc/writing_dynamic_analysis.tex

@@

Determine the instrumentation scheme required by your dynamic analysis, that is,
the kind and format of events to be generated during an instrumented program's
execution. See class \verb+chord.instr.InstrScheme+ for the kinds of supported
events and their formats.

@@

Create a class extending \verb+chord.project.DynamicAnalysis+ and overriding
the appropriate methods in it.

The only method that must be compulsorily overridden is method \verb+getInstrScheme()+,
which must return an instance of the instrumentation scheme chosen in Step 1 above,
plus each \verb+process<event>(<args>)+ method that corresponds to event \verb+<event>+
with format \verb+<args>+ enabled by the chosen instrumentation scheme.
All other methods are no-ops if not overridden.

A sample such class called \verb+MyDynamicAnalysis+ is shown below:

@@

        // User-defined event handlers for this dynamic analysis.
        // No-ops if not overridden.
        public void process<event1>(<args1>) {
            // ***TODO***: User code for handling events of kind <event1> with format <args1>.
        }
        ...
        public void process<eventN>(<argsN>) {
            // ***TODO***: User code for handling events of kind <eventN> with format <argsN>.
        }
    }
\end{verbatim}

@@

Determine the runtime event handler for your dynamic analysis. There are two kinds of runtime event
handlers, offline and online; see package \verb+chord.runtime+ for more details.

For most dynamic analyses, an offline event hander suffices, in which case you don't need to do
anything in this step (except that you may want to change the default values of system properties
\verb+chord.trace.pipe+ and \verb+chord.trace.block.size+ for performance; see
Section \ref{sec:chord-sysprops} for the meaning of these properties). Otherwise, you need to
create a class extending class \verb+chord.runtime.Runtime+ and override the appropriate methods
in it, and provide the fully-qualified name of the created class as the value of system property
\verb+chord.runtime.class+ (whose default value is the class \verb+chord.runtime.BufferedRuntime+).

@@

Compile the analysis by placing the directory containing class \verb+MyDynamicAnalysis+ created
above in the path defined by system property \verb+chord.java.analysis.path+.

@@

Provide the IDs of program runs to be generated (say 1, 2, ..., M) and the command-line arguments to be
used for the program in each of those runs (say <args1>, ..., <argsM>) via system properties
\verb+chord.run.ids=1,2,...,N+ and \verb+chord.args.1=<args1>+, ..., \verb+chord.args.M=<argsM>+.

By default, \verb+chord.run.ids=0+ and \verb+chord.args.0=""+, that is, the program will be run only
once (using run ID 0) with no command-line arguments.

@@

To run the analysis, set system property \verb+chord.run.analyses=<name-of-analysis>+ where
\verb+<name-of-analysis>+ is the name that was provided in the \verb+@Chord+ annotation for class
\verb+MyDynamicAnalysis+ created above.

>>>>

Follow the following steps to write your own dynamic analysis.

@@

Determine the instrumentation scheme required by your dynamic analysis, that is,
the kind and format of events to be generated during an instrumented program's
execution. See Section \ref{sec:instr-events} 
for the kinds of supported events and their formats.

@@

Create a class extending \code{chord.project.DynamicAnalysis} and override
the appropriate methods in it.
The only method that must be compulsorily overridden is method \code{getInstrScheme()},
which must return an instance of the instrumentation scheme chosen in Step 1 above,
plus each \code{process<event>(<args>)} method that corresponds to event \code{<event>}
with format \code{<args>} enabled by the chosen instrumentation scheme.
All other methods are no-ops if not overridden.

A sample such class called \code{MyDynamicAnalysis} is shown below:

@@

        // User-defined event handlers for this dynamic analysis.
        // No-ops if not overridden.
        public void process<event1>(<args1>) {
            // ***TODO***: User code for handling events of kind
            // <event1> with format <args1>.
        }
        ...
        public void process<eventN>(<argsN>) {
            // ***TODO***: User code for handling events of kind
            // <eventN> with format <argsN>.
        }
    }
\end{verbatim}

@@

Determine the runtime event handler for your dynamic analysis. There are two kinds of runtime event
handlers, offline and online; see package \code{chord.runtime} for more details.

For most dynamic analyses, an offline event hander suffices, in which case you don't need to do
anything in this step.
Otherwise, you need to create a class extending \code{chord.runtime.Runtime} and override the
appropriate methods in it, and provide the fully-qualified name of the created class as the value of property
\code{chord.runtime.class} (whose default value is \code{chord.runtime.BufferedRuntime}).

@@

Compile the analysis by placing the directory containing class \code{MyDynamicAnalysis} created
above in the path defined by property \code{chord.java.analysis.path}.

@@

Provide the IDs of program runs to be generated (say 1, 2, ..., M) and the command-line arguments to be
used for the program in each of those runs (say \code{<args1>}, ..., \code{<argsM>}) via properties
\code{chord.run.ids=1,2,...,N} and \code{chord.args.1=<args1>}, ..., \code{chord.args.M=<argsM>}.
By default, \code{chord.run.ids=0} and \code{chord.args.0=""}, that is, the program will be run only
once (using run ID 0) with no command-line arguments.

@@

To run the analysis, set property \code{chord.run.analyses} to \code{<name-of-analysis>}
(recall that \code{<name-of-analysis>} is the name provided in the \code{@Chord} annotation for class
\code{MyDynamicAnalysis} created above).

%(except that you may want to change the default values of properties
%\code{chord.trace.pipe} and \code{chord.trace.block.size} for performance, or the default values
%of properties \code{chord.trace.pipe} and \code{chord.reuse.trace} for determinism across; see
%Section \ref{sec:chord-sysprops} for the meaning of these properties).
